---
title: "W2LECTURE-240124"
author: "niyun"
date: "2024-01-24"
output: 
  github_document:
      toc: true
      toc_depth: 2
      fig_width: 7
      fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in data
```{r}
wk2_stocks <- readRDS("wk2_stocks.rds")
str(wk2_stocks)
```

## Statistics on returns
```{r}
sum(wk2_stocks$SPY_returns) * 100
mean(wk2_stocks$SPY_returns) * 100
sd(wk2_stocks$SPY_returns) * 100
```

+ The cumulative returns of the S&P index during this period is `r round(sum(wk2_stocks$SPY_returns) * 100, 2)`%

+ The average daily returns of the S&P index during this period is `r round(mean(wk2_stocks$SPY_returns) * 100, 2)`%

+ The standard deviation of the daily returns of the S&P index during this period is `r round(sd(wk2_stocks$SPY_returns) * 100, 2)`%

## S&P Prices
```{r message = FALSE, warning = FALSE}
library(tidyverse) 
ggplot(data = wk2_stocks, aes(x = date, y = SPY_prices)) + geom_line()
```

## S&P Yearly Returns
```{r}
wk2_stocks %>%
  mutate(year = year(date)) %>% 
  filter (year <= 2013) %>%
  group_by(year) %>%
  summarize(yr_return = sum(SPY_returns)) %>%
  ggplot(aes(x = year, y = yr_return)) + geom_col()
```
